%% This is an example first chapter.  You should put chapter/appendix that you
%% write into a separate file, and add a line \include{yourfilename} to
%% main.tex, where `yourfilename.tex' is the name of the chapter/appendix file.
%% You can process specific files by typing their names in at the 
%% \files=
%% prompt when you run the file main.tex through LaTeX.
\chapter{An Introduction to our Dark Universe}

\section{Introduction}
"Our whole universe was in a hot dense state,
then nearly fourteen billion years ago expansion started..."Every time I listen to the song from the hot drama "the big bang theory", it make me recall my fascination about the process that our universe went through with a bunch of miracle, and in the end, I can sit here and write the thesis for my master degree. At the starting, there is just a very hot, dense initial state stationing in our universe, Suddenly, it blows off in an extremely short time. In finale, the abundant light elements, the cosmological microwave background(CMB) as well as the large-scale structure are presented in our universe.\\

From the modern astrophysical point of view, our universe consists of three parts of the things, including the material, the dark matter. and also the dark energy. Unfortunately, now we only get the material acknowledged. Basically, we only understand about 4\% of our universe! How to unveil the mystery of the dark matter is now the most popular topic around the world.\\

In this chapter, I will first give a brief introduction about the history of cosmological model of our universe, leading to two "missing mysteries", encompassing "missing energy(dark energy)" and "missing mass(dark matter)". Then, some of the evidence from astrophysics on the dark matter will be performed. \\

